Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-25 paper.tex
up

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} employ GA for semi-automated web service composition considering semantic matchmaking quality and QoS, where the semantic matchmaking quality is measured through evaluating semantic links, which requires a formal definition of ontology in Description Logic. This evaluation model takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach work \cite{fanjiang2014semantic} employs a sequence of fitness functions are used in the binary selection of chromosomes, where semantic matchmaking quality is evaluate in two fitness functions considering concept similarity and parameter similarity respectively, but . The work \cite{pop2009immune} as an immune-inspired web service composition approach employ indirect representation that a binary alphabet to encode a planning graph, where the semantic matchmaking quality is measured by the similarity using information retrieval technique.

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches. There is a lack of a general approaches that achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model to fill the gaps, and then we proposed a PSO-based method with explicit support for the comprehensive model to find optimal compositions.

@@

The aim of web service composition considered in this paper is to automatically select the optimal solutions in considering both QoS and semantic matchmaking quality by a user's request. The request is to provide inputs and obtain outputs, the composition results that should meet the optimal requirements above. A motivating example of this problem is shown in Fig \ref{motivation}. The figure is a DAG represent a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}. This is a classic example of travel planning problem for scholars who seek for booking services of airplanes, buses and hotels reservation, and also generating tourist maps for the conference city. The graph also contains edges that marked with connecting outputs and inputs, which represent valid semantic matches where the outputs of a web service can be passed as the inputs of its successors.

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.25]{motivation.pdf}}
 \caption{ An example of a web service composition}
 \label{motivation}
\end{figure}QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid}

Although obtaining a correct combination of web service is essential, there are many ways to chain web services to reach users' needs with different web services from a service repository. These web services have different QoS in terms of different availability, price, reliability and response time. Moreover, valid semantic matches between two web services could also have different matchmaking quality. For example, Generate Map service produce StreetMap which is considered to be a valid semantic match to TouristMap from users' perspectives. These perspectives are captured in a taxonomy Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for a travel planning domain. For example, the concept Map and its sub-concept urbanMap are assigned with a touristMap instance and streetMap instance respectively in Fig .\ref{taxonomy}. The valid semantic match is considered that an instance of urban Map can be an instance of Map, but not vice versa. However, if a web service $GenerateTouristMap$ is found in the service repository that produces TouristMap as an output, but price is "16.87". I consider its semantic matchmaking quality is higher than the service $GenerateMap$, but price negatively contributes to the overall QoS. Therefore, automatically generating solutions in considering both QoS and matchmaking quality is a very challenging problem.

@@

We herein give formal definitions of the assumptions the concepts regarding the semantic web service composition problem utilised in our approach that consists of four main concepts: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.
\vspace{0.3cm}

@@

\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{(C, Taxonomy) \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.

\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$. $I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$. $QoS_S = \{ t_s, c_s, r_s, a_s, ... \} $ is a set of non-functional attributes of $S$, it typically refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}. $\mathcal{SR}$ is a service repository consisting of a set of $S$, where all the $S$ are registered.
\vspace{0.3cm}

\textbf{Semantic Matchmaking Model}. The mechanism to compose web services relays on the semantic descriptions of inputs and outputs, which enable inputs of a service to be matched by outputs of another. To measure the quality of these matches, we utilise different matchmaking types (\textit{exact, plugin subsumes and fail} \cite{paolucci2002semantic} ) into consideration for exploiting the semantics of inputs and outputs.

\textbf{Definition 3.} Given $a, b \in C$, $type(a, b)$ returns the matchmaking types of two concepts, and this matchmaking type is determined by the logic described in the $O$. If both $a$ and $b$ are equivalent, $exact$ type ($a \equiv b$) is returned. If the concept of $a$ is a sub-concept of the concept of $b$ type ($a \sqsubseteq b$) is returned. If the concept of $a$ is a super-concept of the concept of $b$, $subsumes$ type ($a \sqsupseteq b$) is returned. If none of previous matchmaking types are returned, $fail$ type ($a \perp b$) is returned.

We use the $type(a, b)$ to define full matchmaking between two concept-related input and output of two services.

>>>>

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the semantic matchmaking quality is measured through evaluating the quality of semantic links that require a formal definition of ontology in Description Logic. This evaluation model takes huge cost and time for the domain experts to establish required ontology. Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow. The work \cite{pop2009immune} is an automated immune-inspired web service composition approach, where an indirect representation that a binary alphabet is used to encode a planning graph. However, this composition method is only evaluated on a set of scenarios.

In summary, despite a large number of approaches for semantic web service composition and QoS-aware service composition approaches, there is a lack of a fully automated semantic web service composition approach to optimse semantic matchmaking quality and QoS simultaneously. Therefore, we first propose a general comprehensive quality model that aims to achieve a better semantic matchmaking quality with a slight trade-off in QoS, and then we propose an automated PSO-based approach with explicit support for the comprehensive model to find optimal service compositions.

@@

The aim of web service composition considered in this paper is to automatically compose optimal solutions in considering both QoS and semantic matchmaking quality based on a user's request. The request is to provide inputs and obtain outputs. The resulting composition of this request is a composition solution with an optimal comprehensive quality in terms of semantic matchmaking quality and QoS. A motivating example of this problem is shown in Fig \ref{motivation}. The figure shows a DAG that represents a solution with four web services involved for a request $R$ as a composition task, where inputs of the task are \{TravelDepartureDate, HomeCity, ConferenceCity, TravelReturnDate \} and outputs are \{BusTicket, FlightTicket, TouristMap, HotelReservation \}. This is a classic example of travel planning problem for people who seek for booking services of airplanes, buses and hotels reservation, and also generating tourist maps for the conference city. The graph also contains edges that marked with connected outputs and inputs of two connected atomic services, which represent valid semantic matches that the outputs of a web service can be passed as the inputs of its successors.

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.25]{motivation.pdf}}
 \caption{ An example of a web service composition}
 \label{motivation}
\end{figure}

Although obtaining a correct combination of web service is essential, there are many ways to connect multiple web services chosen from a service repository. These web services provide different QoS in terms of availability, price, reliability and response time. Moreover, valid semantic matches between two connected web services could also have different matchmaking quality. For example, $Generate Map$ service produce $StreetMap$ which is considered to be a valid semantic match to $TouristMap$, while $Bus Service$ produce $BusTicket$ which is considered to be a better valid semantic match to $BusTicket$. The descriptions of these matched resources are captured in a taxonomy depicted in Fig .\ref{taxonomy}, where all the inputs and the outputs related to the web services are described for a travel planning problem. For example, the concept $Map$ and its sub-concept $urbanMap$ are assigned with a $touristMap$ instance and $streetMap$ instance respectively in Fig .\ref{taxonomy}. The valid semantic match is considered that an instance of $urban Map$ can be an instance of $Map$, but not vice versa. To demonstrate the motivation of proposing a comprehensive quality, we give a simple example. The service $GenerateMap$ with a output ($StreetMap$) and a price (``6.72") in the web service composition can be replace by a service $GenerateTouristMap$ with a different output ($TouristMap$) and a different price (``16.87") availabile in the service repository. This composition solution results in a better semantic matchmaking quality, but price negatively contributes to the QoS. Therefore, we need to measure these changes to the solutions considering matchmaking quality and QoS simultaneously for automatically generated solutions.

@@

We herein give formal definitions of the concepts regarding the semantic web service composition problem utilised in our approach, and these concepts are captured in serveral models: a semantic web service model, a semantic matchmaking model, a weighted DAG composition model, and QoS calculation model, and composition problem model.

@@

\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{ C \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.

\textbf{Definition 2.} A semantic web service is defined as a tuple $S = \{ I_{S}, O_{S}, QoS_S \}$ $\in$ $\mathcal{SR}$, where $I_{S}$ is a set of service inputs that must be satisfied to invoke $S$, and $O_{S}$ is a set of service outputs returned by the execution of $S$. $I_{S}$ and $O_{S}$ are concept-related instances that are linked to the concepts $I^{C}_{S}$ and $O^{C}_{S}$, where $ I^{C}_{S}, O^{C}_{S}  \subseteq C$. $QoS_S = \{ t_s, c_s, r_s, a_s, ... \} $ is a set of non-functional attributes of $S$, it refers to response time $t_s$, cost $c_s$, reliability $r_s$, and availability $a_s$ \cite{zeng2003quality}. $\mathcal{SR}$ is a service repository consisting of a set of $S$.
\vspace{0.3cm}

\textbf{Semantic Matchmaking Model}. The mechanism to compose web services relies on the semantic descriptions of inputs and outputs, which enable inputs of a service to be matched by outputs of another. To measure the quality of these matches, we utilise different matchmaking types (\textit{exact, plugin subsumes and fail} \cite{paolucci2002semantic} ).

\textbf{Definition 3.} Given $a, b \in C$, $type(a, b)$ returns the matchmaking types of two concepts, and this matchmaking type is determined by the logic relationship described in the $O$. If both $a$ and $b$ are equivalent, $exact$ type ($a \equiv b$) is returned. If the concept of $a$ is a sub-concept of the concept of $b$ type ($a \sqsubseteq b$) is returned. If the concept of $a$ is a super-concept of the concept of $b$, $subsumes$ type ($a \sqsupseteq b$) is returned. If none of previous matchmaking types are returned, $fail$ type ($a \perp b$) is returned.

We use the returns of $type(a, b)$ to define a full matchmaking considerd in the scenario of connecting two services through concept-related output and concept-related input.
